A weighted sampling algorithm for the design of RNA sequences with targeted secondary structure and nucleotides distribution

### 2013-03-12 ISMB/results_ISMB.tex
fix caption and fig identity nb_sols

\begin{figure*}[ht!]
	\centering
	\includegraphics[width=\textwidth]{Figures/nb_sols_entropy}
	\caption{Number of solutions generated with \ourprog+\RNAinverse. and their average sequence identity. 
	The second row is the sequence identity for a $10\%$\GC and the last for $30\%$\GC inside the base pairs. }
%	\caption{Number of solutions generated by \ourprog and their average sequence identity. The curves are parameterized by the {\GCContent} of the sequences. The data are plotted vs. the length of the target (left), density of stacked base pairs (centre) and number of unpaired nucleotides  in loops (right).}
	\label{fig:nb_sols_entropy}
\end{figure*}

>>>>

\begin{figure*}[ht!]
	\centering
	\includegraphics[width=\textwidth]{Figures/nb_sols_seq_identity.png}
	\caption{Number of solutions generated with \ourprog+\RNAinverse on the first row and their average sequence identity on the second.} 
%	\caption{Number of solutions generated by \ourprog and their average sequence identity. The curves are parameterized by the {\GCContent} of the sequences. The data are plotted vs. the length of the target (left), density of stacked base pairs (centre) and number of unpaired nucleotides  in loops (right).}
	\label{fig:nb_sols_entropy}
\end{figure*}
